Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-05-20 cvx-flats-neurips21/cvx-flats.tex
Updating table again and adding content into 3.1

  \raf{Notes}
  The pred dim of a surrogate is...
  We present a new tool based on property elicitation to study the prediction dimension of surrogate loss functions.
  Our tool unifies... including continuous vs discrete.
  New result in risk measures...
  FSD...

@@

While implicitly observed in some of the literature~\citep{steinwart2008support}\jessie{Add more}, we can observe that consistency implies indirect elicitation.
Formal definitions and the following proof are deferred to Appendix~\ref{sec:consis-implies-indir}, but we loosely mean that converging to the optimal surrogate loss in expectation over the data distribution $\D \sim \X \times \Y$ implies that we can apply a link to the convergent sequence and approach the optimal target loss or conditional statistical value.
\jessie{Make restateable}
\begin{proposition}\label{thm:consistent-implies-indir-elic}
	For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma: \P \toto \R$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
\end{proposition}

@@

\begin{SCtable}
\begin{tabular}{|c|c|}
	\hline
	\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
	% standard tikz coordinate definition using x, y, z coords
	\coordinate (orig) at (0,0,0);

@@

	\begin{scope}
	\clip (h) -- (m) -- (l) -- (h);
	\draw[myblue] (1/2,1/2,0) -- (1/2, 0, 1/2);
	\draw[myblue] (0,1/2,1/2) -- (1/2, 0, 1/2);
	\draw[myblue] (0,1/2,1/2) -- (1/2,1/2, 0);
	\draw[myorange, dashed] (1/2,0,1/2) -- (0,1,0);
	\draw[myorange, dashed] (2/3,1/3,0) -- (0,1/3,2/3);
	\node (uniformdot) at (1/3,1/3,1/3) {$\bullet$};
	%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
	\end{scope}
	\node[inner sep=2pt] (levset1) at (3/4,1/8,1/8) {$\Gamma_{1}$};
	\node[inner sep=2pt] (levsetabs) at (5/12,5/12,1/6) {$\Gamma_{\bot}$};
	%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
	%\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
	\placefiglabel{(Q1)}
	\end{tikzpicture}
	&
	\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
	% standard tikz coordinate definition using x, y, z coords
	\coordinate (orig) at (0,0,0);

@@

	\begin{scope}
	\clip (h) -- (m) -- (l) -- (h);
	\draw[myblue,thin] (2/3,0,1/3) -- (0,2/3, 1/3);
	\def\e{1/16};
	\draw[myblue,thin] (\e + 1/3, 1/3- \e,1/3) -- (1/2 + \e, 1/2 - \e,0);
	\coordinate (point) at (1/3 - \e/2, 1/3 + \e, 1/3 - \e/2);
	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (1/4,3/4,0) -- (point);
	\draw[orange, dashed] (2/3 + \e/2,0,1/3 - \e/2) -- (0,2/3 + \e/2, 1/3 - \e/2);
	\node at (point) {$\bullet$};
	%\draw[orange, very thick] (0.3,0.7,0) -- (0.3,0.7,2);
	%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
	\end{scope}
	\node[inner sep=2pt] (levsetmin1) at (2/3, 1/6,1/6) {$\Gamma_{-1}\!\!$};
	\node[inner sep=2pt] (levset1) at (1/6,2/3,1/6) {$\Gamma_{1}\!\!$};
	%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
	%\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
	\placefiglabel{(Q2)}
	\end{tikzpicture}
	\\
	\hline
  \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
% standard tikz coordinate definition using x, y, z coords
\coordinate (orig) at (0,0,0);

@@

\begin{scope}
\clip (h) -- (m) -- (l) -- (h);
\foreach \c in {0,0.05,...,1}
{
	\pgfmathsetmacro\aa{\c}
	\coordinate (A) at ($(\aa,1-\aa,0)$);
	\coordinate (B) at ($(\aa,1-\aa,2)$);
	\draw[myblue,thin] (A) -- (B);
}
\draw[orange, very thick,dashed] (0.5,0.5,0) -- (0,0.,2);
%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
\end{scope}
\node (centerdot) at (1/3,1/3,1/3) {$\bullet$};
\node[inner sep=2pt] (levset1) at (0.5,0.5, -0.3) {$\Gamma_{0}\!$};
%\node[inner sep=2pt] (levset2) at (0.7,0.3,-.3) {$\Gamma_{\!\!-0.4}\!\!\!\!$};
%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.5,0.5,0);
\placefiglabel{(Q3)}
\end{tikzpicture}
&
\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
% standard tikz coordinate definition using x, y, z coords
\coordinate (orig) at (0,0,0);

@@

\begin{scope}
\clip (h) -- (m) -- (l) -- (h);
\foreach \c in {0,0.1,...,1}
{
	\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
	\pgfmathsetmacro\bb{0.5*\c}
	\coordinate (A) at ($(\aa,1-\aa,0)$);
	\coordinate (B) at ($(1-\aa,\aa,0)$);
	\coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
	\draw[myblue,thin] (C) parabola (A);
	\draw[myblue,thin] (C) parabola (B);
}
\def\c{0.6}
\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
\pgfmathsetmacro\bb{0.5*\c}
\coordinate (A) at ($(\aa,1-\aa,0)$);
\coordinate (B) at ($(1-\aa,\aa,0)$);
\coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
\coordinate (Cleft) at ($(\bb + 2,\bb,1-2*\bb)$);
\coordinate (Cright) at ($(\bb,\bb + 2,1-2*\bb)$);
\coordinate (centerdot) at (0.3,0.3, 0.4);
\draw[myorange, very thick] (C) parabola (A);
\draw[myorange, very thick] (C) parabola (B);
\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (3/4,0,1/4) -- (centerdot);
\node at (centerdot) {$\bullet$};
\end{scope}
\def\c{0.6}
\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
\pgfmathsetmacro\bb{0.5*\c}
\node (levset) at (0.5,0.5,-.3) {$\Gamma_{0.6}$};
\draw[-latex,thin] (levset) edge[in=270,out=180] ($(\aa,1-\aa,0)$);
\draw[-latex,thin] (levset) edge[in=270,out=0] ($(1-\aa,\aa,0)$);
\placefiglabel{(Q4)}
\end{tikzpicture}
\\
\hline
\end{tabular}\label{tab:quadrants-simplices}
\caption{Example properties for each of the quadrants. 
In (Q1), we fix $p$ uniform in the abstain level set $\Gamma_\bot$. 
We cannot fit a line ($1$-flat) through $p$ without leaving the level set $\Gamma_\bot$.  
Therefore, there is no $1$-dimensional consistent convex surrogate for abstain by Lemma~\ref{lem:convex-flats-inf-dim}.  
(Q2) is similar to (Q1) but has no target loss since it is not elicitable.
In (Q3), we can fit a $1$-flat through any $p \in \simplex$ for least squares, eliciting expected value.
In (Q4), we look at the variance, and take the distribution $p = \bullet \in \Gamma_{0.6}$.
Since $\Gamma_{0.6}$ (solid orange) is curved, we cannot draw a $1$-flat contained in the level set, and conclude there is not a $1$-dimensional consistent convex surrogate w.r.t. the variance.
}
\end{SCtable}

@@

\jessie{Suggest cutting this for space if needed, since it's in the table.}
\paragraph{Example: Variance.}
As a warm-up, let us see how to show $\eliccvx(\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} using that variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
Interestingly, while perhaps intuitively obvious, even this simple result is novel.
In particular, the well-known fact that the variance is not elicitable does not yield a lower bound of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.

\begin{corollary}
  \label{cor:variance}
  Let $\P$ be a set of continuous Lebesgue densities on $\Y=\reals$ with all $p \in \P$ having the same support.
  If there exist $p,q,q'\in\P$ with $\E_p Y = \E_q Y \neq \E_{q'} Y$ and $\Var(p) \neq \Var(q)$,
  \btw{Raf: I think this condition is tight actually: if there is no such triple in $\P$, I think $\eliccvx(\Var) \leq 1$ (i.e., $\Var$ is constant or a function of the mean)}
  then $\conscvx(\Var)=\eliccvx(\Var)=2$.
\end{corollary}
\begin{proof}
  For the upper bound, we may elicit the first two moments via the convex loss $L(r,y) = (r_1-y)^2 + (r_2-y^2)^2$, and recover the variance via $\psi(r) = r_2-r_1^2$, giving $\eliccvx(\Var) \leq 2$.
  Now for the lower bound.
  Without loss of generality, $\E_qY < \E_{q'}Y$.
  Let $r = \tfrac 1 2 \E_qY + \tfrac 1 2 \E_{q'}Y$, and define $V:\Y\to\reals, y\mapsto y-r$.
  Then $\zeros{V} = \{p'\in\P \mid \E_{p'}Y=r\} = \Gamma_r$ where $\Gamma:p'\mapsto \E_{p'}Y$ is the mean.
  As $\E_q Y < r < \E_{q'} Y$, we conclude $\E_q V < 0 < \E_{q'} V$.
  We have now satisfied Condition~\ref{cond:v-interior} for $d=1$.
  To apply Theorem~\ref{thm:bayes-risk-lower-bound}, it remains to show that $\Var$ is non-constant on $\Gamma_r$.
  % and the identity $\Var(p') = \E_{p'} Y^2 - (\E_{p'} Y)^2$
  By our assumptions and the definition of $\Var$, we have $\E_p Y^2 \neq \E_q Y^2$.
  Letting $p_1 = \tfrac 1 2 q + \tfrac 1 2 q'$, $p_2 = \tfrac 1 2 p + \tfrac 1 2 q'$, we have $\E_{p_i}Y = r$ for $i\in\{1,2\}$, but $\E_{p_1} Y^2 = \tfrac 1 2 \E_qY^2 + \tfrac 1 2 \E_{q'}Y^2 \neq \tfrac 1 2 \E_pY^2 + \tfrac 1 2 \E_{q'}Y^2 = \E_{p_2}Y^2$.
  As $p_1,p_2$ have the same mean but different second moments, we conclude $\Var(p_1) \neq \Var(p_2)$.
\end{proof}

\paragraph{Example: Conditional Value at Risk.}

@@

\jessie{Comment on how this lets us ``shift'' Q1 to Q2, and Q3 to Q4.  This is a subtlety missing in Table~\ref{tab:quadrants-simplices} too.}
%Lemma~\ref{lem:consistent-loss-implies-prop} confirms that consistency with respect to a target property is a strictly broader notion than with respect to a target loss.
Because each target loss in $\L$ elicits some property, but not all target properties can be elicited by a loss (e.g. the variance), consistency with respect to a property is the strictly broader notion.
This points to indirect elicitation as a natural necessary condition for consistency, as formalized in Theorem \ref{thm:consistent-implies-indir-elic}.

\begin{theorem}\label{thm:consistent-implies-indir-elic}
	For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma: \P \toto \R$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
	\jessie{Move to prop; give credit to literature}
\end{theorem}

@@

\paragraph{Example: High-confidence classification.}\label{subsec:examples-finite}
Given the target loss $\ell^{abs}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$,  we can consider the \emph{abstain property} it elicits, where one predicts the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
\citet{ramaswamy2016convex} present a convex surrogate for the abstain loss that takes as input a prediction whose dimension is logarithmic in the number of outcomes, yielding new upper bounds on $\conscvx(\ell^{abs})$ which are an exponential improvement over previous results, e.g.,~\cite{crammer2001algorithmic}.

@@

>>>>

  \raf{Notes}
  The prediction dimension of a surrogate is the lowest dimension $d$ such that we can construct a convex surrogate $L : \reals^d \times \Y \to \reals$ that is consistent with respect to a given prediction task.
  We present a new tool based on property elicitation to study the prediction dimension of surrogate loss functions.
  Our tool unifies results on prediction dimension for various settings, including continuous vs discrete predictions.
  We apply our tool in continuous estimation settings to yield a new lower bound on prediction dimension in risk measures, resolving a stated open question in the literature~\citep{frongillo2015elicitation}.
  In discrete prediction settings, this tool also recovers previous lower bounds on prediction dimension attained by feasible subspace dimension~\citep{ramaswamy2016convex}.

@@

While implicitly observed in some of the literature~\citep{steinwart2008support}\jessie{Add more}, we can observe that consistency implies indirect elicitation.
Formal definitions and the following proof are deferred to Appendix~\ref{sec:consis-implies-indir}, but we loosely mean that converging to the optimal surrogate loss in expectation over the data distribution $\D \sim \X \times \Y$ implies that we can apply a link to the convergent sequence and approach the optimal target loss or conditional statistical value.

\begin{restatable}{proposition}{consistencyimpliesindirelic}\label{thm:consistent-implies-indir-elic}
	For a surrogate $L \in \L$, if the pair $(L, \psi)$ is consistent with respect to a property $\gamma: \P \toto \R$ or a loss $\ell$ eliciting $\gamma$, then $(L, \psi)$ indirectly elicits $\gamma$.
\end{restatable}

@@

\paragraph{Q1: Abstain}
The abstain target loss is a well-studied variation of 0-1 loss that allows for an ``abstain'' report that gives a lesser punishment $\alpha \in (0,1)$ for abstaining, $r = \bot$.
Given the target loss $\ell^{\alpha}(r,y) := \Ind{r \not \in \{y, \bot\}} + \alpha\Ind{r = \bot}$,  we can consider the \emph{abstain property} $\gamma$ it elicits, where one predicts the most likely outcome $y$ if $Pr[Y=y|x] \geq 1-\alpha$ and ``abstain'' by predicting $\bot$ otherwise.
\citet{ramaswamy2016convex} present a convex surrogate for the abstain loss with $\alpha = 1/2$ that takes as input a prediction whose dimension is logarithmic in the number of outcomes, yielding new upper bounds on $\conscvx(\ell^{1/2})$ which are an exponential improvement over previous results, e.g.,~\citep{crammer2001algorithmic,rifkin2004defense}.

When $n =3$, the property $\gamma$ elicited by $\ell^{1/2}$ is depicted in Table~\ref{tab:quadrants-simplices} (Q1).
Upon closer inspection, the level set boundaries are found at the set of distribution where is a $y$ such that $p_y = 1/2 = 1-\alpha$.
For any distribution $p \in \relint{\gamma_\bot}$, we can derive a lower bound on convex consistency dimension by trying to fir a $1$-flat through this point; however, by the global geometry of the property and location of the abstain cell relative to other cells, we cannot fit a $1$-flat (line in the 2-d projection of the simplex here) fully contained in $\gamma_\bot$ that passes through $p = \bullet$.

\paragraph{Q2: High confidence classification}
Consider the following scenario where someone is deciding how to dress for the weather based on a meteorologist's forecast: a forecaster is choosing between three outcomes $\Y = \{$rainy, sunny, snowy$\}$, and we suppose we want to have some bias towards health and safety, so the meteorologist should only predict sunny weather if $Pr[$sunny $|$ weather data$] \geq 3/4$.
Otherwise, they should predict whatever is more likely  given the weather data: rain or snow.

We can now model this problem by a property with the reports $\R = \Y$, and have 
\begin{align*}
\gamma(p) &= \begin{cases}
\text{sunny} & p_{\text{sunny}} \geq 1/2 \\
\text{rainy} & p_{\text{sunny}} \leq 1/2 \wedge p_{\text{rainy}} \geq p_{\text{snowy}} \\
\text{snowy} & p_{\text{sunny}} \leq 1/2 \wedge p_{\text{snowy}} \geq p_{\text{rainy}} \\
\end{cases}~,~
\end{align*}

This property is shown in Table~\ref{tab:quadrants-simplices} (Q2), and we can observe the point $p = \bullet = (0.3,0.3,0.4)$ that, like abstain, we cannot fit a $1$-flat entirely contained in the level set $\gamma_{\text{snowy}}$ through $p$.

\paragraph{Q3: Least-squares regression}
While least squares regression is commonly used in machine learning and statistics for continuous estimation, it might not be immediately \emph{why} we do so until we study the property estimated by squared loss, which turns out to be the expected value.
With $\Y = \{-1,0,1\}$, we can visualize the level sets of the expected value as in Table~\ref{tab:quadrants-simplices} (Q3).

Since squared loss is a $1$-dimensional loss, we can verify that for all $p \in \simplex$, we can fit a $1$-flat (precisely equal to the level set) through $p$, as demonstrated in the Table.
See Corollary~\ref{cor:variance} in Appendix~\ref{app:omitted-examples} to see our framework applied to derive lower bounds for convex consistency dimension of the variance.

\paragraph{Q4: Variance}
\paragraph{Example: Variance.}
As a warm-up, let us see how to show $\eliccvx(\Var)=2$, meaning the lowest dimension of a convex loss to estimate conditional variance is 2. %~\citep{osband1985providing,lambert2018elicitation}.
This lower bound will follow from Theorem~\ref{thm:bayes-risk-lower-bound} using that variance is the Bayes risk of squared loss $L(r,y) = (r-y)^2$, which elicits the mean $\Gamma(p) = \E_p Y$.
Interestingly, while perhaps intuitively obvious, even this simple result is novel.
In particular, the well-known fact that the variance is not elicitable does not yield a lower bound of 2, as it does not rule out the variance being a link of a real-valued convex-elicitable property; cf.~\citet[Remark 1]{frongillo2020elicitation}.

\begin{SCtable}
\begin{tabular}{c|c}
	%\hline
	\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
	% standard tikz coordinate definition using x, y, z coords
	\coordinate (orig) at (0,0,0);

@@

	\begin{scope}
	\clip (h) -- (m) -- (l) -- (h);
	\draw[myblue] (1/2,1/2,0) -- (1/2, 0, 1/2);
	\draw[myblue] (0,1/2,1/2) -- (1/2, 0, 1/2);
	\draw[myblue] (0,1/2,1/2) -- (1/2,1/2, 0);
	\coordinate (point) at (0.3,0.4, 0.3);
	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (1/4,3/4,0) -- (point);
	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0.7,0,0.3) -- (point);
	\node at (point) {$\bullet$};
	%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
	\end{scope}
	\node[inner sep=2pt] (levset1) at (3/4,1/8,1/8) {$\gamma_{y_1}\!\!$};
	\node[inner sep=2pt] (levsetabs) at (5/12,5/12,1/6) {$\gamma_{\bot}$};
	%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
	%\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
	\placefiglabel{(Q1)}
	\end{tikzpicture}
	&
	\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
	% standard tikz coordinate definition using x, y, z coords
	\coordinate (orig) at (0,0,0);

	\pgfmathsetmacro{\ph}{0.54}
	\pgfmathsetmacro{\pm}{0.23}
	\pgfmathsetmacro{\pl}{0.23}
	\coordinate (p) at (\ph,\pm,\pl);
	\coordinate (uniform) at (1/3,1/3,1/3);
	\coordinate[label=below:${\text{rainy}}$] (h) at (1,0,0);
	\coordinate[label=below:${\text{sunny}}$] (m) at (0,1,0);
	\coordinate[label=right:${\text{snowy}}$] (l) at (0,0,1);

@@

	\begin{scope}
	\clip (h) -- (m) -- (l) -- (h);
	\draw[myblue,thin] (1/2,0,1/2) -- (0,1/2, 1/2);
	\def\e{1/16};
	\draw[myblue] (1/4,1/4,1/2) -- (1/2, 1/2, 0);
	\coordinate (point) at (0.3,0.4, 0.3);
	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0.4, 0.6, 0.) -- (point);
	\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (0,0.4,0.6) -- (point);
	\node at (point) {$\bullet$};
	%\draw[orange, very thick] (0.3,0.7,0) -- (0.3,0.7,2);
	%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
	\end{scope}
	\node[inner sep=2pt] (levsetmin1) at (2/3, 1/6,1/6) {$\gamma_{\text{rainy}}$};
	\node[inner sep=2pt] (levset1) at (1/6,2/3,1/6) {$\gamma_{\text{snowy}}$};
	%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
	%\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.3,0.7,0);
	\placefiglabel{(Q2)}
	\end{tikzpicture}
	\\
	\hline
  \begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
% standard tikz coordinate definition using x, y, z coords
\coordinate (orig) at (0,0,0);

@@

\begin{scope}
\clip (h) -- (m) -- (l) -- (h);
\foreach \c in {0,0.05,...,1}
{
	\pgfmathsetmacro\aa{\c}
	\coordinate (A) at ($(\aa,1-\aa,0)$);
	\coordinate (B) at ($(\aa,1-\aa,2)$);
	\draw[myblue,thin] (A) -- (B);
}
\draw[orange, thick,dashed] (0.45,0.55,0) -- (0.45,.55,2);
%\draw[orange, very thick] (0.7,0.3,0) -- (0.7,0.3,2);
\end{scope}
\node (point) at (0.3,0.4,0.3) {$\bullet$};
\node[inner sep=2pt] (levset1) at (0.45,0.55, -0.3) {$\Gamma_{0.05}\!$};
%\node[inner sep=2pt] (levset2) at (0.7,0.3,-.3) {$\Gamma_{\!\!-0.4}\!\!\!\!$};
%\draw[-latex,thin] (levset2) edge[in=270,out=90] (0.7,0.3,0);
\draw[-latex,thin] (levset1) edge[in=270,out=90] (0.45,0.55,0);
\placefiglabel{(Q3)}
\end{tikzpicture}
&
\begin{tikzpicture} [scale=\tikzfigscale, thick, tdplot_main_coords]
% standard tikz coordinate definition using x, y, z coords
\coordinate (orig) at (0,0,0);

@@

\begin{scope}
\clip (h) -- (m) -- (l) -- (h);
\foreach \c in {0,0.1,...,1}
{
	\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
	\pgfmathsetmacro\bb{0.5*\c}
	\coordinate (A) at ($(\aa,1-\aa,0)$);
	\coordinate (B) at ($(1-\aa,\aa,0)$);
	\coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
	\draw[myblue,thin] (C) parabola (A);
	\draw[myblue,thin] (C) parabola (B);
}
\def\c{0.6}
\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
\pgfmathsetmacro\bb{0.5*\c}
\coordinate (A) at ($(\aa,1-\aa,0)$);
\coordinate (B) at ($(1-\aa,\aa,0)$);
\coordinate (C) at ($(\bb,\bb,1-2*\bb)$);
\coordinate (Cleft) at ($(\bb + 2,\bb,1-2*\bb)$);
\coordinate (Cright) at ($(\bb,\bb + 2,1-2*\bb)$);
\coordinate (centerdot) at (0.3,0.3, 0.4);
\draw[myorange, very thick] (C) parabola (A);
\draw[myorange, very thick] (C) parabola (B);
\draw[orange, dashed,shorten >= -3cm, shorten <=-3cm] (3/4,0,1/4) -- (centerdot);
\node at (centerdot) {$\bullet$};
\end{scope}
\def\c{0.6}
\pgfmathsetmacro\aa{0.5*(sqrt(1-\c)+1)}
\pgfmathsetmacro\bb{0.5*\c}
\node (levset) at (0.5,0.5,-.3) {$\Gamma_{0.6}$};
\draw[-latex,thin] (levset) edge[in=270,out=180] ($(\aa,1-\aa,0)$);
\draw[-latex,thin] (levset) edge[in=270,out=0] ($(1-\aa,\aa,0)$);
\placefiglabel{(Q4)}
\end{tikzpicture}
%\\
%\hline
\end{tabular}\label{tab:quadrants-simplices}
\caption{Example properties for each of the quadrants. 
In (Q1), we fix $p$ uniform in the abstain level set $\Gamma_\bot$. 
We cannot fit a line ($1$-flat) through $p$ without leaving the level set $\Gamma_\bot$.  
Therefore, there is no $1$-dimensional consistent convex surrogate for abstain by Lemma~\ref{lem:convex-flats-inf-dim}.  
(Q2) is similar to (Q1) but has no target loss since it is not elicitable.
In (Q3), we can fit a $1$-flat through any $p \in \simplex$ for least squares, eliciting expected value.
In (Q4), we look at the variance, and take the distribution $p = \bullet \in \Gamma_{0.6}$.
Since $\Gamma_{0.6}$ (solid orange) is curved, we cannot draw a $1$-flat contained in the level set, and conclude there is not a $1$-dimensional consistent convex surrogate w.r.t. the variance.
}
\end{SCtable}

@@

\paragraph{Conditional Value at Risk.}

@@

\jessie{Comment on how this lets us ``shift'' Q1 to Q2, and Q3 to Q4.  This is a subtlety missing in Table~\ref{tab:quadrants-simplices} too.}
%Lemma~\ref{lem:consistent-loss-implies-prop} confirms that consistency with respect to a target property is a strictly broader notion than with respect to a target loss.
Because each target loss in $\L$ elicits some property, but not all target properties can be elicited by a loss (e.g. the variance), consistency with respect to a property is the strictly broader notion.
This points to indirect elicitation as a natural necessary condition for consistency, as formalized in Proposition~\ref{thm:consistent-implies-indir-elic}.

\consistencyimpliesindirelic*

@@

\paragraph{Example: High-confidence classification.}\label{subsec:examples-finite}
Recall the abstain target loss $\ell^{abs}(r,y) := \Ind{r \not \in \{y, \bot\}} + (1/2)\Ind{r = \bot}$,  we can consider the \emph{abstain property} it elicits, where one predicts the most likely outcome $y$ if $Pr[Y=y|x] \geq 1/2$ and ``abstain'' by predicting $\bot$ otherwise.
\citet{ramaswamy2016convex} present a convex surrogate for the abstain loss that takes as input a prediction whose dimension is logarithmic in the number of outcomes, yielding new upper bounds on $\conscvx(\ell^{abs})$ which are an exponential improvement over previous results, e.g.,~\cite{crammer2001algorithmic}.

@@

\subsection{Variance (Q4)}
\begin{corollary}
	\label{cor:variance}
	Let $\P$ be a set of continuous Lebesgue densities on $\Y=\reals$ with all $p \in \P$ having the same support.
	If there exist $p,q,q'\in\P$ with $\E_p Y = \E_q Y \neq \E_{q'} Y$ and $\Var(p) \neq \Var(q)$,
	\btw{Raf: I think this condition is tight actually: if there is no such triple in $\P$, I think $\eliccvx(\Var) \leq 1$ (i.e., $\Var$ is constant or a function of the mean)}
	then $\conscvx(\Var)=\eliccvx(\Var)=2$.
\end{corollary}
\begin{proof}
	For the upper bound, we may elicit the first two moments via the convex loss $L(r,y) = (r_1-y)^2 + (r_2-y^2)^2$, and recover the variance via $\psi(r) = r_2-r_1^2$, giving $\eliccvx(\Var) \leq 2$.
	Now for the lower bound.
	Without loss of generality, $\E_qY < \E_{q'}Y$.
	Let $r = \tfrac 1 2 \E_qY + \tfrac 1 2 \E_{q'}Y$, and define $V:\Y\to\reals, y\mapsto y-r$.
	Then $\zeros{V} = \{p'\in\P \mid \E_{p'}Y=r\} = \Gamma_r$ where $\Gamma:p'\mapsto \E_{p'}Y$ is the mean.
	As $\E_q Y < r < \E_{q'} Y$, we conclude $\E_q V < 0 < \E_{q'} V$.
	We have now satisfied Condition~\ref{cond:v-interior} for $d=1$.
	To apply Theorem~\ref{thm:bayes-risk-lower-bound}, it remains to show that $\Var$ is non-constant on $\Gamma_r$.
	% and the identity $\Var(p') = \E_{p'} Y^2 - (\E_{p'} Y)^2$
	By our assumptions and the definition of $\Var$, we have $\E_p Y^2 \neq \E_q Y^2$.
	Letting $p_1 = \tfrac 1 2 q + \tfrac 1 2 q'$, $p_2 = \tfrac 1 2 p + \tfrac 1 2 q'$, we have $\E_{p_i}Y = r$ for $i\in\{1,2\}$, but $\E_{p_1} Y^2 = \tfrac 1 2 \E_qY^2 + \tfrac 1 2 \E_{q'}Y^2 \neq \tfrac 1 2 \E_pY^2 + \tfrac 1 2 \E_{q'}Y^2 = \E_{p_2}Y^2$.
	As $p_1,p_2$ have the same mean but different second moments, we conclude $\Var(p_1) \neq \Var(p_2)$.
\end{proof}
